---
title: "Webpropol answers 2020"
author: "Essi Viippola"
date: "7.2.2021"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library("tidyverse")
library("ggplot2")

sys.source("data-preprocessing.R", envir = knitr::knit_global())

```

## Data description

- Number of students: `r likert$student_id %>% unique() %>% length()`
- Number of likert questions: 34
- Number of non-likert questions: 5

The distribution of answers by study year is presented below.

```{r}
ggplot(nonlikert, aes(x=study_group)) + 
  geom_bar() +
  geom_text(stat="count", aes(label=..count..), vjust=-0.5) +
  labs(x="Study group", y="Number of students", title="Number of students by study year")
```

## Likert questions

### Difference between study groups

The first year students seemed to be the most critical in their answer.

```{r}
ggplot(likert %>% filter(!is.na(answer)), aes(x=factor(study_group), y=answer)) + 
  geom_boxplot() + 
  facet_grid(.~question_group) +
  labs(x="Study group", y="Answer", title="Question group-wise answers by study group")
```

```{r}
ggplot(likert %>% filter(!is.na(answer)), aes(x=factor(study_group), y=answer)) + 
  geom_boxplot() + 
  facet_wrap(~as.numeric(question_number)) +
  labs(x="Study group", y="Answer", title="Question-wise answers by study group")
```

```{r}
ggplot(likert %>% filter(study_group==1, !is.na(answer)), aes(x=answer)) + 
  geom_bar() + 
  facet_wrap(~as.numeric(question_number)) +
  labs(x="Answer", y="Count", title="1st year students")
```

```{r}
ggplot(likert %>% filter(study_group==2, !is.na(answer)), aes(x=answer)) + 
  geom_bar() + 
  facet_wrap(~as.numeric(question_number)) +
  labs(x="Answer", y="Count", title="2nd year students")
```

```{r}
ggplot(likert %>% filter(study_group==3, !is.na(answer)), aes(x=answer)) + 
  geom_bar() + 
  facet_wrap(~as.numeric(question_number)) +
  labs(x="Answer", y="Count", title="3rd year students")
```


## Missing data

```{r}
tbl = likert %>% group_by(question_group, study_group) %>% summarize(total_answers = n(), missing_answers = sum(is.na(answer)), missing_pct = round(missing_answers / total_answers * 100, 1))

names(tbl) = c("Question group", "Study group", "Total answers", "Missing answers", "Missing answers (%)")

knitr::kable(tbl)
```


## Onsite vs online learning

`r (nonlikert %>% filter(preferred_method <= 3) %>% nrow() / nonlikert %>% nrow() * 100) %>% round()` % of students preferred onsite learning over online learning.

```{r}
ggplot(nonlikert %>% filter(!is.na(preferred_method)), aes(x=preferred_method, fill=ifelse(preferred_method <= 3, "onsite preferred", "online preferred"))) + 
  geom_bar() + 
  facet_grid(study_group~.) +
  geom_text(stat="count", aes(label=..count..), vjust=-0.5) +
  labs(x="Onsite vs online preferred", y="Students", fill="Preference", title="Students' onsite vs online preference by study group") +
  theme(legend.position = "top")
```
